Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-13 cmsb22.tex
Update the order of authors again

\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Kunihiko Hiraishi\inst{3}\orcidID{0000-0003-1750-1891} \and \\
  Belaid Benhamou\inst{1} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418}
  }

>>>>

\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Belaid Benhamou\inst{1} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418} \and \\
  Kunihiko Hiraishi\inst{3}\orcidID{0000-0003-1750-1891}
  }
